Selecting Team Members of The Female United States Artistic Gymnastics Team at The 2024 Paris Olympics Based on Performance and Stability To Maximize Success

### 2024-01-16 manuscript/submission.tex
removing table midlines

\begin{table}
  \caption{Top ten female candidates for each apparatus based on mean score alone and 
  their $\mu - \alpha \sigma$ parameter values.}
  \label{tab:tableBBP}
\centering
\begin{tabular}[t]{llllllll}
 \toprule
  \multicolumn{2}{c}{BB} & \multicolumn{2}{c}{FX} & \multicolumn{2}{c}{UB} & \multicolumn{2}{c}{VT}\\
  \cmidrule(lr){1-2}\cmidrule(lr){3-4}\cmidrule(lr){5-6}\cmidrule(lr){7-8}
Athlete & $\mu - \sigma$ & Athlete & $\mu - \sigma$ & Athlete & $\mu - 0.5 \sigma$ & Athlete & $\mu - 0.5 \sigma$\\
\midrule
biles & 14.38 & biles & 14.55 & jones & 14.26 & biles & 14.78\\
\midrule
mcclain & 14.14 & lincoln & 13.73 & biles & 14.17 & carey & 14.36\\
\midrule
lee & 13.69 & carey & 13.41 & wong & 13.59 & mcclain & 14.20\\
\midrule
sumanasekera & 12.95 & dicello & 13.4 & matthews & 13.50 & jones & 14.20\\
\midrule
blakely & 12.78 & chiles & 13.38 & blakely & 13.49 & chiles & 14.11\\
\midrule
jones & 12.58 & jones & 13.29 & greaves & 13.47 & sumanasekera & 14.07\\
\midrule
roberson & 12.50 & mcclain & 13.21 & miller & 13.38 & blakely & 14.05\\
\midrule
wong & 12.48 & wong & 13.16 & chiles & 13.34 & dicello & 13.88\\
\midrule
dicello & 12.45 & roberson & 12.98 & zhou & 13.28 & richardson & NA\\
\midrule
frazier & NA & frazier & NA & walker & NA & torry & NA\\
\bottomrule
\end{tabular}
\end{table}

Based on the plot of the top ten female athletes on the balance beam apparatus in figure~\ref{fig:FA} I selected the parameter of 
the score standard deviation subtracted from the mean score in order to identify the best suited five 
athletes. Based on the parameter displayed in table~\ref[tablebbp], the five ``best'' female athletes on balance beam are Biles, McClain, 
Lee, Sumanasekera, and Blakely with Biles and McClain being expert for this apparatus. Similarly, the five ``best'' 
female athletes for floor exercise are Biles, Lincoln, Carey, 
Mcclain, Dicello, Chiles with Biles and Lincoln being expert for this apparatus. Based on the plot of the top ten 
female athletes on the uneven bars apparatus I selected the parameter of 
half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
athletes. Based on the parameter, the five ``best'' female athletes for uneven bars are Jones, Biles, Wong, 
Matthews, and Blakely with Jones and Biles being expert for this apparatus. Similarly, the five ``best'' female 
athletes on vault are Biles, Carey, Mcclain, Jones, 
and Chiles with Biles and Carey being expert for this apparatus.

@@

Based on the plots in figure~\ref{fig:FAA}, it is very clear that Biles is strong candidate to 
compete for the individual all-around medal. However, it is not clear whether Jones or McClain is better suited 
to be the second United States individual all-around candidate. Looking at the data values and plot of the combinations of three athletes, 
it is clear that Biles, Jones, and McClain are by far the best suited trio to compete for the team all-around medal. 
Additionally, since this data suggests that both McClain and Jones should compete in the qualifying round, there 
is no need to select one over the other for the second individual all-around candidate spot as they would both get 
the opportunity to qualify, and their scores at the Olympics will determine which athlete, if either, will qualify 
to attend the individual all-around finals. Looking at plot of the combinations of four athletes, it is not clear whether Chiles, Carey, or 
Blakely is best suited to be the fourth team all-around candidate as their means and standard deviations are very 
similar. However, looking at the individual apparatus events provides justification for who to ultimately select. 
Knowing that two athletes per country can compete for an apparatus medal, it is strategic to try to compose the 
team of the best two United States athletes for each apparatus. Based on the computations and plots, the superior two 
athletes on balance beam are Biles and McClain, the superior two athletes on floor exercise are Biles and Lincoln, 
the superior two athletes on uneven bars are Jones and Biles, and the superior two athletes on vault are Biles 
and Carey. Since Lincoln was not among our top candidates for an all-around medal, it would be logical to select her 
as the fifth United States Olympic team member who does not compete in the all-around qualifying round. Additionally, 
since Carey is one of the candidates being considering for the all-around qualifying round and she is one of our superior 
athletes on vault, it is reasonable to also select her to be the final member of the Olympic team. Although, the 
summed combination that included Carey has the lowest mean in comparison to the combinations including Chiles or 
Blakely, the selection of Carey can be further justified by the facts that the summed mean score difference is 
within one point the combination including Carey has the lowest summed standard deviation.

>>>>

\begin{table}
  \caption{Top ten female candidates for each apparatus based on mean score alone and 
  their $\mu - \alpha \sigma$ parameter values.}
  \label{tab:tableBBP}
\centering
\begin{tabular}[t]{llllllll}
 \toprule
  \multicolumn{2}{c}{BB} & \multicolumn{2}{c}{FX} & \multicolumn{2}{c}{UB} & \multicolumn{2}{c}{VT}\\
  \cmidrule(lr){1-2}\cmidrule(lr){3-4}\cmidrule(lr){5-6}\cmidrule(lr){7-8}
Athlete & $\mu - \sigma$ & Athlete & $\mu - \sigma$ & Athlete & $\mu - 0.5 \sigma$ & Athlete & $\mu - 0.5 \sigma$\\
\midrule
biles & 14.38 & biles & 14.55 & jones & 14.26 & biles & 14.78\\

mcclain & 14.14 & lincoln & 13.73 & biles & 14.17 & carey & 14.36\\

lee & 13.69 & carey & 13.41 & wong & 13.59 & mcclain & 14.20\\

sumanasekera & 12.95 & dicello & 13.4 & matthews & 13.50 & jones & 14.20\\

blakely & 12.78 & chiles & 13.38 & blakely & 13.49 & chiles & 14.11\\

jones & 12.58 & jones & 13.29 & greaves & 13.47 & sumanasekera & 14.07\\

roberson & 12.50 & mcclain & 13.21 & miller & 13.38 & blakely & 14.05\\

wong & 12.48 & wong & 13.16 & chiles & 13.34 & dicello & 13.88\\

dicello & 12.45 & roberson & 12.98 & zhou & 13.28 & richardson & NA\\

frazier & NA & frazier & NA & walker & NA & torry & NA\\
\bottomrule
\end{tabular}
\end{table}

Based on the plot of the top ten female athletes on the balance beam apparatus in Figure~\ref{fig:FA} I selected the parameter of 
the score standard deviation subtracted from the mean score in order to identify the best suited five 
athletes. Based on the parameter displayed in Table~\ref[tableBBP], the five ``best'' female athletes on balance beam are Biles, McClain, 
Lee, Sumanasekera, and Blakely with Biles and McClain being expert for this apparatus. Similarly, the five ``best'' 
female athletes for floor exercise are Biles, Lincoln, Carey, 
Mcclain, Dicello, Chiles with Biles and Lincoln being expert for this apparatus. Based on the plot of the top ten 
female athletes on the uneven bars apparatus I selected the parameter of 
half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
athletes. Based on the parameter, the five ``best'' female athletes for uneven bars are Jones, Biles, Wong, 
Matthews, and Blakely with Jones and Biles being expert for this apparatus. Similarly, the five ``best'' female 
athletes on vault are Biles, Carey, Mcclain, Jones, 
and Chiles with Biles and Carey being expert for this apparatus.

@@

Based on the plots in Figure~\ref{fig:FAA}, it is very clear that Biles is strong candidate to 
compete for the individual all-around medal. However, it is not clear whether Jones or McClain is better suited 
to be the second United States individual all-around candidate. Looking at the data values and plot of the combinations of three athletes, 
it is clear that Biles, Jones, and McClain are by far the best suited trio to compete for the team all-around medal. 
Additionally, since this data suggests that both McClain and Jones should compete in the qualifying round, there 
is no need to select one over the other for the second individual all-around candidate spot as they would both get 
the opportunity to qualify, and their scores at the Olympics will determine which athlete, if either, will qualify 
to attend the individual all-around finals. Looking at plot of the combinations of four athletes, it is not clear whether Chiles, Carey, or 
Blakely is best suited to be the fourth team all-around candidate as their means and standard deviations are very 
similar. However, looking at the individual apparatus events provides justification for who to ultimately select. 
Knowing that two athletes per country can compete for an apparatus medal, it is strategic to try to compose the 
team of the best two United States athletes for each apparatus. Based on the computations and plots, the superior two 
athletes on balance beam are Biles and McClain, the superior two athletes on floor exercise are Biles and Lincoln, 
the superior two athletes on uneven bars are Jones and Biles, and the superior two athletes on vault are Biles 
and Carey. Since Lincoln was not among our top candidates for an all-around medal, it would be logical to select her 
as the fifth United States Olympic team member who does not compete in the all-around qualifying round. Additionally, 
since Carey is one of the candidates being considering for the all-around qualifying round and she is one of our superior 
athletes on vault, it is reasonable to also select her to be the final member of the Olympic team. Although, the 
summed combination that included Carey has the lowest mean in comparison to the combinations including Chiles or 
Blakely, the selection of Carey can be further justified by the facts that the summed mean score difference is 
within one point the combination including Carey has the lowest summed standard deviation.
